Demo arXiv template

### 2022-11-27 paper/paper.qmd
more on the normalising step

<!-- $x(s_i^\prime;t_j) = \sum_{i \in \Omega}x(s_i; t_j)$ -->

@@

@@

$$F_{\eta}(x(\mathbf{s}; \mathbf{t}))$$

@@

The purpose of normalising is for cross-comparison using the normal score.
This step can get criticism from analysts for being unnecessarily forcing the scale to the normal scale.
This step is usually in the end of the pipeline when the data have been processed into a univariate series. 
When the data are not distributed normally, a distributed is usually fitted before converting to the normal score via the normal reverse CDF function: $\Phi^{-1}(.)$: $$\Phi^{-1}[F_{\eta}(x(\mathbf{s}; \mathbf{t}))],$$ where $\eta \in H \subseteq \mathbb{R}^{d_{\eta}}$ is the distribution parameter and $d_{\eta}$ is the number of parameter of $\eta$. 
Sometimes, to account for the monthly variation in the data, the fitting is done separately for each month and the noramlising step can be written as $\Phi^{-1}[F_{\eta}^m(x(\mathbf{s};t_{j^*}))]$, where $j^*$ is all the indexes that satisfy $j^* \mod 12 = m$ for each $m = 0, 1,\cdots, 11$.

>>>>

collect ground and satellite image -> merge
<!-- $x(s_i^\prime;t_j) = \sum_{i \in \Omega}x(s_i; t_j)$ -->

@@

weighting

@@

*modell fit? *

$$F_{\eta}(x(\mathbf{s}; \mathbf{t})),$$ where $\eta \in H \subseteq \mathbb{R}^{d_{\eta}}$ is the distribution parameter and $d_{\eta}$ is the number of parameter of $\eta$.

Considerations need to be given on selecting the best distribution to fit, 
Various discussion on the fitting methods and goodness of fit. 
Potentially, more care about how much difference each combination give in terms of the index value.

sometimes, to account for the monthly variation in the data, the fitting is done separately for each month and the noramlising step can be written as $\Phi^{-1}[F_{\eta}^m(x(\mathbf{s};t_{j^*}))]$, where $j^*$ is all the indexes that satisfy $j^* \mod 12 = m$ for each $m = 0, 1,\cdots, 11$.

@@

This step maps the univariate series into a different scale, typically for the ease of comparison. For example, a normal scale, [0, 1], [0, 100] may be favored to report certain indexes. In drought indexes, i.e. SPI or SPEI, the quantiles from the fitted distribution is converted into the normal scale via the normal reverse CDF function: $\Phi^{-1}(.)$.

Normalising is usually used in the end of the pipeline and its main difference from the scaling step is that here the change of scale also changes the distribution of the variable. 
While being commonly used, this step can get criticism from analysts for forcing the data into the decided scale, which can be either unnecessary or inaccurately exaggerate or downplay the outliers. Also, the use of normal scale needs to be interpreted with caution. @fig-normalising illustrates the normal density not being directly proportional to its probability of occurrence. This is concerning, especially at the extreme values, where a normal density of -5 and -4 has magnitudes of difference into its probability of occurrence (1 in 3,000,000 and 1 in 31,000, respectively).

```{r fig-normalising}
#| fig-cap: "scatterplot of quantile vs. its density values."
library(tidyverse)
all <- tibble(x = seq(-5, 5, 0.01), y = pnorm(x)) 
dt <- tibble(x = c(-5, -4), y = pnorm(x)) 
label <- tibble(x = c(-5, -4), y = pnorm(x), 
                label = c("a chance \nof 1 in \n 3,488,556", "a chance \nof 1 in \n 31,574"))

dt %>% 
  ggplot() + 
  geom_point(aes(x= x, y =y)) + 
  geom_line(data = all, aes(x = x, y =y)) + 
  ggrepel::geom_label_repel(
    data = label, aes(x = x, y = y, label =label), 
    nudge_y = 0.2, arrow = arrow(length = unit(0.08, "inches")), min.segment.length = 0) + 
  scale_x_continuous(breaks = seq(-5, 5, 1)) + 
  xlab("Density") + 
  ylab("Quantile") + 
  theme_bw() + 
  theme(panel.grid.minor = element_blank())
```

### 2022-11-27 paper/paper.tex
more on the normalising step

\ifdefined\Shaded\renewenvironment{Shaded}{\begin{tcolorbox}[interior hidden, boxrule=0pt, enhanced, breakable, borderline west={3pt}{0pt}{shadecolor}, sharp corners, frame hidden]}{\end{tcolorbox}}\fi

@@

@@

\[F_{\eta}(x(\mathbf{s}; \mathbf{t}))\]

@@

The purpose of normalising is for cross-comparison using the normal
score. This step can get criticism from analysts for being unnecessarily
forcing the scale to the normal scale. This step is usually in the end
of the pipeline when the data have been processed into a univariate
series. When the data are not distributed normally, a distributed is
usually fitted before converting to the normal score via the normal
reverse CDF function: \(\Phi^{-1}(.)\):
\[\Phi^{-1}[F_{\eta}(x(\mathbf{s}; \mathbf{t}))],\] where
\(\eta \in H \subseteq \mathbb{R}^{d_{\eta}}\) is the distribution
parameter and \(d_{\eta}\) is the number of parameter of \(\eta\).
Sometimes, to account for the monthly variation in the data, the fitting
is done separately for each month and the noramlising step can be
written as \(\Phi^{-1}[F_{\eta}^m(x(\mathbf{s};t_{j^*}))]\), where
\(j^*\) is all the indexes that satisfy \(j^* \mod 12 = m\) for each
\(m = 0, 1,\cdots, 11\).

>>>>

\ifdefined\Shaded\renewenvironment{Shaded}{\begin{tcolorbox}[interior hidden, borderline west={3pt}{0pt}{shadecolor}, boxrule=0pt, breakable, sharp corners, enhanced, frame hidden]}{\end{tcolorbox}}\fi

@@

collect ground and satellite image -\textgreater{} merge

@@

\emph{modell fit? }

\[F_{\eta}(x(\mathbf{s}; \mathbf{t})),\] where
\(\eta \in H \subseteq \mathbb{R}^{d_{\eta}}\) is the distribution
parameter and \(d_{\eta}\) is the number of parameter of \(\eta\).

Considerations need to be given on selecting the best distribution to
fit, Various discussion on the fitting methods and goodness of fit.
Potentially, more care about how much difference each combination give
in terms of the index value.

sometimes, to account for the monthly variation in the data, the fitting
is done separately for each month and the noramlising step can be
written as \(\Phi^{-1}[F_{\eta}^m(x(\mathbf{s};t_{j^*}))]\), where
\(j^*\) is all the indexes that satisfy \(j^* \mod 12 = m\) for each
\(m = 0, 1,\cdots, 11\).

@@

This step maps the univariate series into a different scale, typically
for the ease of comparison. For example, a normal scale, {[}0, 1{]},
{[}0, 100{]} may be favored to report certain indexes. In drought
indexes, i.e.~SPI or SPEI, the quantiles from the fitted distribution is
converted into the normal scale via the normal reverse CDF function:
\(\Phi^{-1}(.)\).

Normalising is usually used in the end of the pipeline and its main
difference from the scaling step is that here the change of scale also
changes the distribution of the variable. While being commonly used,
this step can get criticism from analysts for forcing the data into the
decided scale, which can be either unnecessary or inaccurately
exaggerate or downplay the outliers. Also, the use of normal scale needs
to be interpreted with caution. Figure~\ref{fig-normalising} illustrates
the normal density not being directly proportional to its probability of
occurrence. This is concerning, especially at the extreme values, where
a normal density of -5 and -4 has magnitudes of difference into its
probability of occurrence (1 in 3,000,000 and 1 in 31,000,
respectively).

{\centering \includegraphics{paper_files/figure-pdf/fig-normalising-1.pdf}

\caption{\label{fig-normalising}scatterplot of quantile vs.~its density
values.}
